Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-09-19 manuscript/paper-tycho.tex
Refactor profile/FWHM fits, alter folder structure
Separate profile prep (error calculation, etc) from profile fitting and
FWHM computation.  Refactored FWHM code (in vein of full model code),
change FWHM and profile fit intermediate data format.
Pickle/json model fit outputs, table generation
Code and utilities to save simple/full model fit outputs
Directories structured accordingly.  New ipynb for profile/spectra
figures and tables.  A bit more paper work.

\begin{abstract}
\note[Aaron]{Copy pasted from NASA abstract, not reviewed} Young supernova
remnants may exhibit thin (~1--10\% of shock radius) X-ray rims of synchrotron
radiation from forward shock-accelerated electrons that travel downstream of
the shock and quickly cease to radiate. Rim widths limited by radiative energy
losses should decrease with energy and require magnetic field amplification
$10$--$100\times$ that expected from adiabatic shock compression.  Damped
magnetic fields behind rims may produce thin rims without strong field
amplification but require energy-independent rim widths. We measured rim widths
around Tycho's supernova remnant in 5 energy bands using a 750 ks \Chandra
observation. Rims narrow with increasing energy, favoring loss-limited
radiation over magnetic damping. Observed widths are best fit by electron
transport models requiring amplified magnetic fields $\abt0.1$--$1$ mG and
particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work
on SN 1006. Inferred magnetic fields, diffusion coefficients, and
diffusion-energy scaling may constrain models for cosmic ray acceleration in
supernova remnants and plasma turbulence in astrophysical shocks.
\end{abstract}

@@

% TODO go through and double check tenses.
We measured synchrotron rim full widths at half maximum (FWHMs) from an
archival \Chandra ACIS-I observation of Tycho
(RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
between 2009 Apr 11 and 2009 May 5 (PI: John P. Hughes;
\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}).
The total exposure time was $734 \unit{ks}$.
Level 1 \Chandra data were reprocessed with CIAO 4.6 and CALDB 4.6.1.1 and kept
unbinned with ACIS spatial resolution $0.492\arcsec$.
Merged and corrected events were divided into five energy bands:
0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
We excluded 1.7--2 keV energy range to avoid the \ion{Si}{13} (He$\alpha$)
emission line at 1.85 keV, prevalent in the remnant's thermal ejecta, which
\remove[Brian]{could} \remove[Aaron]{would} \add[Aaron]{may}
\note[Aaron]{since some profiles are practically uncontaminated?}
contaminate our nonthermal profile measurements.

@@

\begin{figure}
    \centering
    %\plotone{figures/f0-snr.pdf}
    \includegraphics[width=0.35\textwidth]{figures/f0-snr.pdf}
    \caption{RGB image of Tycho with region selections overlaid.  Bands are
    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).
    \note[Aaron]{Temporary figure; regions need re-numbering.}
    \note[Aaron]{We could show the spectrum extraction regions on here too?
    Maybe too cluttered.}}
    \label{fig:snr}
\end{figure}

All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function.

@@

We extracted spectra for all regions to check that rim width measurements are
not affected by contaminating thermal line emission.  In each region, we
selected upstream and downstream sections \note[Aaron]{any better word than
`section'?} from which to extract spectra.
The upstream section is the smallest sub-region that contains the measured FWHM
bounds from all energy bands (see Section~\ref{sec:fwhms}); i.e., this region
captures the thin rim.
The downstream section extends from the back of the rim (where the upstream
section ends) to the rim model fit's
(equation~\eqref{eq:prof}) downstream limit.
Figure~\ref{fig:spec} plots an example profile (4.5--7 keV) with the
downstream and upstream sections highlighted; the dividing line is set at the
\textbf{???--???} energy band's downstream FWHM limit (see Figure~\ref{fig:profiles}).
Background spectra were extracted from circular regions around the remnant's
exterior \note[Aaron]{give size in arcsec?}; each region's spectra used the
closest background region's spectrum \note[Aaron]{a bit awkward}.

% TODO must match fig:profiles!  Keep both figures' region numbers updated and
% consistent.
\begin{figure}
    \plotone{figures/f0-spec.pdf}
    \caption{Example spectra and fits from Region 1. Left: example profile
    ($4.5$--$7 \unit{keV}$) with highlighted downstream (blue) and upstream
    (grey) sections. These sections are fixed for Region 1, regardless of
    energy band (to be absolutely clear).  Middle: downstream spectrum with
    fitted absorbed power law; Si and S lines at $1.85$, $2.45 \unit{keV}$ are
    clearly visible.  Right: upstream spectrum with fitted absorbed power law
    shows that the thin rim is not contaminated by line emission.}
    \label{fig:spec}
\end{figure}

We fit $0.5$--$7 \unit{keV}$ spectra from each region's upstream and downstream
sections to an absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) with
spectral index $n$, hydrogen column density $n_H$, and a normalization as free
parameters.  Table~\ref{tab:spec} lists best fit parameters and reduced
$\chi^2$s for all regions.  Spectra from thin rims (upstream sections) are
well-fit by the power law model alone; spectra from sections downstream of the
rims are generally poorly-fit, reflecting thermal contamination primarily from
\ion{Si}{13} and \ion{S}{15} He$\alpha$ line emission at $1.85$ and $2.45$ keV.
Although most downstream spectra show thermal contamination, some regions
(e.g., 3, 4 on Tycho's northwestern limb) are reasonably well-fit by an
absorbed power law as well due to a larger distance between the forward shock
and contact discontinuity.
Upstream spectra fits spectral indices between $2.5$--$3$ are consistent with
synchrotron radiation spectra for ???? population of electrons
\note[Aaron]{citation for e- distr. indices?}. Best fit column densities have
range ($0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$) consistent with previous
fits to Tycho's nonthermal rims \citep{hwang2002} but somewhat larger than
values reported from radio and optical? HI absorption line measurements
($\abt0.5 \times 10^{22}$ in radio \citep{albinson1986} per \citet{hwang2002};
$\abt0.35 \times 10^{22}$ by \citet{kothes2004}, $\abt 0.4 \times 10^{22}$ from
extinction--gas ratio (references in \citet{black1984})...).
% TODO keep stated ranges of spectral indices, column densities up to date

\note[Aaron]{On rob's suggestion of fitting thermal model -- can we get away
with just fitting line emission and constraining from there? or is the
whole NEI apparatus needed.  If we add thermal components -- report spectral
indices and show better fit / spectral softening (confirmation)?}

% TODO short script to build table from saved spectra fits
% TODO keep region numbers updated (discussion of good/bad downstream spectra)
\begin{table}
    \scriptsize
    \centering
    \caption{Absorbed power law fit parameters for all regions' upstream and
    downstream spectra.  The reduced $\chi^2$ values for upstream spectrum fits
    are consistent with a lack of thermal emission, whereas downstream spectra
    are often poorly-fit by an absorbed power law due to line
    emission (e.g., Figure~\ref{fig:spec}).\label{tab:spec}}
    \input{tab-spec.tex}
\end{table}

Table~\ref{tab:spec} confirms that our region selections are practically free
of thermal line emission, as already suggested by visual inspection
(Figure~\ref{fig:snr}).  Our exclusion of all $1.7$--$2
\unit{keV}$ photons should further limit any thermal contamination, as
the $1.85 \unit{keV}$ Si line emission is over a third of Tycho's thermal flux
as detected by \Chandra \citep{hwang2002}.  We may safely proceed to model our
measured rim widths as being due entirely to nonthermal radiation
\note[Aaron]{horrid phrasing}.

@@

% TODO keep mentioned number of regions updated!
% TODO regions 2,3; 6,7 should be stretched forward a little more
%      just to be more consistent (just from eyeballing...)
We obtained radial intensity profiles from $\abt 10$--$20\arcsec$ behind the
shock to $\abt 2$--$8\arcsec$ in front for each of our 13 regions in all five
energy bands.  To increase signal-to-noise, we integrate along the shock ($\abt
8$--$24\arcsec$) in each region.  \note[Aaron]{Box dimensions are all over the
place} Plotted and fitted profiles are reported in vignetting and
exposure-corrected \note[Aaron]{double check CIAO guides} intensity units;
error bars are computed from raw count data assuming Poisson statistics.
Intensity profiles peak sharply (within $\abt 2$--$3\arcsec$) behind the shock,
demarcating our thin rims, and then fall off until thermal emission from ejecta
picks up at Tycho's contact discontinuity \citep{warren2005}.

@@

\begin{figure*}[ht]
    \plotone{figures/f0-prfs.pdf}
    \caption{Profile fits for Region 1}
    \label{fig:profiles}
\end{figure*}

% TODO do all the work, but with different FWHM calculation -- to confirm
%      that it doesn't make a big difference...
% TODO subtract $\min(C_u, C_d)$ from profiles before getting FWHM, then
%      come back and edit the text.
% TODO keep region numbers here updated!
From the fitted profiles we extracted a full width at half maximum (FWHM) for
each region and each energy band.  We could not resolve a FWHM in regions 2, 6,
8, 9, and 11 at 0.7--1 keV (Table~\ref{tab:fwhms}); in these regions, either
the downstream FWHM bound would extend outside the fit domain or we could not
find an acceptable fit to equation~\eqref{eq:prof}.  We were able to resolve
FWHMs for all regions at higher energy bands (1--7 keV).

@@

% Fit data to models
We fitted the two transport models given by Equations~\eqref{eq:simp-mod} and
\eqref{eq:full-mod} to our measured rim widths as a function of energy.
Although our profiles are summed counts from a continuous energy range, we
assigned each width measurement to the lower energy limit of its band
(e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
model profile widths at $0.7 \unit{keV}$). \note[Aaron]{bad wording}
We also average the positive and negative error bars on each FWHM measurement
(Table~\ref{tab:fwhms}) for least squares fitting.
% Averaging/merging/synthesizing, somehow, our results
Rim widths from each region are fitted separately; we consider filament and
remnant-wide physical parameters by averaging best fit parameters for each
region in Section~\ref{sec:fit-results}.

% Model knobs and how we twiddled them
We have three parameters to vary (more if we consider magnetic damping).
They are diffusion-energy scaling exponent $\mu$, normalized diffusion
coefficient $\eta_2$, and magnetic field strength $B_0$.
Explain why we are fixing $\mu$ (forward reference best fit figures).
We consider $\mu = 0, 1/3, 1/2, 1, 3/2, 2$; recall that $\mu = 1/3$ and $1/2$
respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
energy spectra.  Explain why we also give results with $\eta_2$ fixed at $1$.

A few remnant-specific parameters enter into the model calculations.  We take
electron spectral index $s = 2.3$ (from radio spectral index $\alpha = 0.65$,
\citet{kothes2006} \note[Aaron]{not using $0.58$ from Green's catalog?!}),
remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
a factor of 2; we interpolate the data of \citet{williams2013} to estimate
individual shock velocities for each of our regions.
\note[Aaron]{this might belong in Section~\ref{sec:transport}?}

@@

% TODO give individual regions' FWHMs and m_E values
\begin{table*}[ht]
    \scriptsize
    \centering
    \caption{Averaged filaments NO UPDATE THIS\label{tab:fwhms}}
    \input{tab-fwhms-ave-arith.tex}
    \input{tab-fwhms-ave-geom.tex}
    \tablecomments{Errors computed as standard errors of mean, see text}
\end{table*}

% -------------------------
% Model fit results, tables
% -------------------------
\subsection{Model fit results}
\label{sec:fit-results}

@@

% Averaged fit results
In each filament, we averaged best fit parameters $B_0$, $\eta_2$ from each
constituent region to obtain filament-wide estimates on $B_0$ and $\eta_2$,
reported in Table~\ref{tab:fits-avg}.  Stated uncertainties are standard errors
of the mean \note[Aaron]{may need to scale by $\abt 2 \times$ to get 1-sigma
confidence interval since our sample sizes are so small}.  We note that both
averages and errors are strongly affected by outliers from extreme best fit
values, as can be seen in Table~\ref{tab:fits-all} -- especially as the typical
number of regions per filament (i.e., our sample size) is quite small.

@@

>>>>

\begin{abstract}
\note[Aaron]{Copy pasted from NASA abstract, not reviewed} Young supernova
remnants may exhibit thin ($\abt1$--$10$\% of shock radius) X-ray rims of synchrotron
radiation from forward shock-accelerated electrons that travel downstream of
the shock and quickly cease to radiate. Rim widths limited by radiative energy
losses should decrease with energy and require magnetic field amplification
$10$--$100\times$ that expected from adiabatic shock compression.  Damped
magnetic fields behind rims may produce thin rims without strong field
amplification but require energy-independent rim widths. We measured rim widths
around Tycho's supernova remnant in 5 energy bands using a 750 ks \Chandra
observation. Rims narrow with increasing energy, favoring loss-limited
radiation over magnetic damping. Observed widths are best fit by electron
transport models requiring amplified magnetic fields $\abt0.1$--$1$ mG and
particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work
on SN 1006. Inferred magnetic fields, diffusion coefficients, and
diffusion-energy scaling may constrain models for cosmic ray acceleration in
supernova remnants and plasma turbulence in astrophysical shocks.
\end{abstract}

@@

% NOTE go through and double check tenses.
We measured synchrotron rim full widths at half maximum (FWHMs) from an
archival \Chandra ACIS-I observation of Tycho
(RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
between 2009 Apr 11 and 2009 May 5 (PI: John P. Hughes;
\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}).
The total exposure time was $734 \unit{ks}$.
Level 1 \Chandra data were reprocessed with CIAO 4.6 and CALDB 4.6.1.1 and kept
unbinned with ACIS spatial resolution $0.492\arcsec$.
Merged and corrected events were divided into five energy bands:
0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
We excluded 1.7--2 keV energy range to avoid the \ion{Si}{13} (He$\alpha$)
emission line at 1.85 keV, prevalent in the remnant's thermal ejecta, which
\remove[Brian]{could} \remove[Aaron]{would} \add[Aaron]{may}
\note[Aaron]{since some profiles are practically uncontaminated?}
contaminate our nonthermal profile measurements.

@@

% NOTE generate final, higher quality figure + newer figure for regions-5
\begin{figure}
    \centering
    %\plotone{figures/f0-snr.pdf}
    \includegraphics[width=0.35\textwidth]{figures/f0-snr.pdf}
    \caption{RGB image of Tycho with region selections overlaid.  Bands are
    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).
    \note[Aaron]{Could show the spectrum extraction regions on here too?
    Maybe too cluttered.}}
    \label{fig:snr}
\end{figure}

All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function.
Looking at proposer's guide, Figure 4.13 -- the off-axis PSF should
still have FWHM of $\abt 1\arcsec$ at $4\arcmin$ (approx. Tycho's radius).
Is that good enough for us?

@@

% NOTE be consistent in usage of word 'sections'
We extracted spectra for all regions to check that rim width measurements are
not affected by contaminating thermal line emission.  In each region, we
selected upstream and downstream sections from which to extract spectra.  The
upstream section is the smallest sub-region that contains the measured FWHM
bounds from all energy bands (see Section~\ref{sec:fwhms}); i.e., this region
captures the thin rim.  The downstream section extends from the back of the rim
(end of the upstream section) to the rim model fit's (equation~\eqref{eq:prof})
downstream limit.  We merged spectra from all \Chandra ObsIDs and grouped the
data into bins of $\geq 15$ counts.  Figure~\ref{fig:spec} plots an example
profile (4.5--7 keV) with the downstream and upstream sections highlighted; the
dividing line is set at the \textbf{???--???} energy band's downstream FWHM
limit here (see Figure~\ref{fig:profiles}).
We extracted background spectra from circular regions (radius $\abt 30\arcsec$)
around the remnant's exterior; each thin rim region was matched to the closest
background region's spectrum.
% Background region size is valid for data-tycho/bkg-2/ selections

% NOTE must match fig:profiles!  Keep region numbers updated and
% consistent.  Currently, region 1 of data-tycho/regions-4/ selections
\begin{figure*}
    \plotone{figures/fig-specs.pdf}
    \caption{Spectra and fits from Region 1. Left: $4.5$--$7 \unit{keV}$
    profile with highlighted downstream (blue) and upstream (grey) sections.
    Intensity units are arbitrary (a.u.).  Middle: downstream spectrum with
    absorbed power law fit; Si and S lines at $1.85$, $2.45 \unit{keV}$ are
    clearly visible.  Right: upstream spectrum with absorbed power law fit
    shows that the filament is likely free of thermal line emission.}
    \label{fig:spec}
\end{figure*}

We fit $0.5$--$7 \unit{keV}$ spectra from each region's upstream and downstream
sections to an absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) with
spectral index $n$, hydrogen column density $n_H$, and a normalization as free
parameters.  Table~\ref{tab:spec} lists best fit parameters and reduced
$\chi^2$ values for all regions.  Spectra from thin rims (upstream sections)
are well-fit by the power law model alone; spectra from sections downstream of
the rims are generally poorly-fit, reflecting thermal contamination primarily
from \ion{Si}{13} and \ion{S}{15} He$\alpha$ line emission at $1.85$ and $2.45$
keV.  Although most downstream spectra show thermal contamination, some regions
(e.g., 4, 5 on Tycho's northwestern limb) are reasonably well-fit downstream by
an absorbed power law as well due to a larger distance between the forward
shock and contact discontinuity.
Upstream spectra fits spectral indices between $2.5$--$3$ are consistent with
synchrotron radiation spectra for ???? population of electrons
\note[Aaron]{citation for e- distr. indices?}. Best fit column densities from
upstream spectra, between $0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$, are
consistent with previous fits to Tycho's nonthermal rims \citep{hwang2002} but
somewhat larger than $\abt0.35$--$0.5 \times 10^{22}$ from radio and optical??
HI absorption line measurements \citep{black1984, albinson1986, kothes2004}.
% NOTE keep stated ranges of spectral indices, column densities up to date

\note[Aaron]{On rob's suggestion of fitting thermal model -- can we get away
with just fitting line emission and constraining from there? or is the
whole NEI apparatus needed.  If we add thermal components -- report spectral
indices and reconfirm spectral softening?}

% NOTE keep region numbers updated (in discussion of good/bad downstream spectra)
\begin{table}
    \scriptsize
    \centering
    \caption{Absorbed power law fit parameters for all regions' upstream and
    downstream spectra.  The reduced $\chi^2$ values for upstream spectrum fits
    are consistent with a lack of thermal emission, but values for downstream
    fits indicate a poor fit due to line emission.
    \label{tab:spec}}
    \input{tab-spec.tex}
\end{table}

Table~\ref{tab:spec} confirms that our region selections are practically free
of thermal line emission, as already suggested by visual inspection
(Figure~\ref{fig:snr}).  Our exclusion of all $1.7$--$2
\unit{keV}$ photons should further limit any thermal contamination, as
the $1.85 \unit{keV}$ Si line emission is over a third of Tycho's thermal flux
as detected by \Chandra \citep{hwang2002}.  We may safely proceed to model our
measured rim widths as being due entirely to nonthermal radiation
\note[Aaron]{bad phrasing}.

@@

% NOTE keep mentioned number of regions updated!
% TODO regions 2,3; 6,7 should be stretched forward a little more in regions-5
%      just to be more consistent (just from eyeballing...)
We obtained radial intensity profiles from $\abt 10$--$20\arcsec$ behind the
shock to $\abt 2$--$8\arcsec$ in front for each of our 13 regions in all five
energy bands.  To increase signal-to-noise, we integrate along the shock ($\abt
8$--$24\arcsec$) in each region.  Plotted and fitted profiles are reported in
vignetting and exposure-corrected, but arbitrary, intensity units; error bars
are computed from raw count data assuming Poisson statistics.  Intensity
profiles peak sharply (within $\abt 2$--$3\arcsec$) behind the shock,
demarcating our thin rims, and then fall off until thermal emission from ejecta
picks up at Tycho's contact discontinuity \citep{warren2005}.

@@

\begin{figure*}[ht]
    \plotone{figures/fig-profiles.pdf}
    \caption{Best fit profiles with measured FWHMs demarcated for each energy
             band in Region 1.  Red data points are excluded from profile fit
             domain.}
    \label{fig:profiles}
\end{figure*}

% NOTE keep blacklisted/excluded region numbers updated!
From the fitted profiles we extracted a full width at half maximum (FWHM) for
each region and each energy band.  We could not resolve a FWHM in regions 2, 6,
and 8 at 0.7--1 keV (Table~\ref{tab:fwhms}); in these regions, either
the downstream FWHM bound would extend outside the fit domain or we could not
find an acceptable fit to equation~\eqref{eq:prof}.  We were able to resolve
FWHMs for all regions at higher energy bands (1--7 keV).
% NOTE review the FWHM rejection criterion, on the final set of regions

@@

% Fit data to models
We fit the two transport models given by Equations~\eqref{eq:simp-mod} and
\eqref{eq:full-mod} to our measured rim widths as a function of energy.
Although our measured radial profiles sum a continuous energy range of counts,
we assigned each width measurement to the lower energy limit of its band
(e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
model profile widths at $0.7 \unit{keV}$) \note[Aaron]{bad wording}.
We also averaged the positive and negative error bars on each FWHM measurement
(Table~\ref{tab:fwhms}) for least squares fitting.
% Averaging/merging/synthesizing, somehow, our results
Rim widths from each region are fitted separately; we consider filament and
remnant-wide physical parameters by averaging best fit parameters for each
region in Section~\ref{sec:fit-results}.

% Model knobs and how we twiddled them
We have three parameters to vary (more if we consider magnetic damping).
They are diffusion-energy scaling exponent $\mu$, normalized diffusion
coefficient $\eta_2$, and magnetic field strength $B_0$.
Explain why we are fixing $\mu$ (forward reference best fit figures).
We consider $\mu = 0$, 1/3, 1/2, 1, 1.5, and 2; recall that $\mu = 1/3$ and $1/2$
respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
energy spectra.  As $\eta_2$ is highly variable in our fits, we also consider
fits with $\eta_2 = 1$ fixed, coincident with Bohm diffusion at $2 \unit{keV}$.

A few remnant-specific parameters enter into the model calculations.  We take
electron spectral index $s = 2.3$ (from radio spectral index $\alpha = 0.65$,
\citet{kothes2006} \note[Aaron]{not using $0.58$ from Green's catalog?!}),
remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
a factor of 2; we interpolated shock velocities reported by
\citet{williams2013} to estimate individual shock velocities for each region.
\note[Aaron]{this paragraph might belong in Section~\ref{sec:transport}?}

@@

% TODO give individual regions' FWHMs and m_E values
\begin{table*}[ht]
    \tiny
    \centering
    \caption{FWHMs for all regions.\label{tab:fwhms}}
    %\input{tab-fwhms-ave-arith.tex}
    %\input{tab-fwhms-ave-geom.tex}
    \input{tab-fwhms.tex}
\end{table*}

% -------------------------
% Model fit results, tables
% -------------------------
\subsection{Model fit results}
\label{sec:fit-results}
% TODO do all the work, but with different FWHM calculation -- to confirm
%      that it doesn't make a big difference...

@@

% Averaged fit results
In each filament, we averaged best fit parameters $B_0$, $\eta_2$ from each
constituent region to obtain filament-wide estimates on $B_0$ and $\eta_2$,
reported in Table~\ref{tab:fits-avg}.  Stated uncertainties are standard errors
of the mean \note[Aaron]{may need to scale by $\abt 2 \times$ to get 1-sigma
confidence interval since our sample sizes are so small}.  We note that both
averages and errors are strongly affected by outliers from extreme best fit
values, as can be seen in Table~\ref{tab:fits} -- especially as the typical
number of regions per filament (i.e., our sample size) is quite small.

@@

\subsection{Variations on a theme of plug \& chug}

Explain briefly, effects (percentage change or similar?) of model fit parameter
changes, results if we vary Tycho distance to $2.3 \unit{kpc}$ or $4
\unit{kpc}$; see \citet{hayato2010}.

Is it worth discussing effects of various twiddle-ables: compression ratio $r$,
accounting for azimuthal variation in $v_s$ (compare to taking a remnant
average)?  Sean already discussed $E_{\mt{cut}}$ (result: more high energy
elections to damp out widening effect at high energy).

(YES, ADD THIS TO DRAFT -- MAY AS WELL)

Any azimuthal variations -- need the table of filament averaged parameters
first, and possibly smaller regions.
